%!TEX root=../main.tex


\section{Related Work}

Almost every framework, that gets published in a paper compares itself to other, similar frameworks. 
Hence there already exists some information on the relative performance between frameworks. 
However, many of the most common frameworks today have been released many years ago. 
Because of that, three problems arise.
First, the comparisons are based on very old versions of the frameworks, with no information on the current behaviour available. 
And second, many of the other frameworks are no longer in use because they were replaced by something else, making the comparisons difficult to interpret.
Third, the evaluations are performed by those developing the frameworks, which always implies some kind of bias.
We are thus providing an objective benchmark on the current state of the most commonly used graph analysis frameworks. 

The comparisons often include PowerGraph or Apache's Spark GraphX, two frameworks that we did not include in our testing.

In 2013 \cite{Galois} Galois was last compared to GraphLab, PowerGraph and Ligra in a shared memory setting. The results of their comparison are mainly, that Galois outperforms Ligra on BFS and SSSP on most graphs. Meanwhile, performance of Ligra and Galois on PR is similar but very dependent on the graph. In some cases, Ligra outperforms Galois, on other graphs Galois is faster than Ligra.

About 5 years afterwards the capability of executing distributed was added to Galois through Gluon \cite{vertGalois}. 
There distributed Galois is being compared to Gemini and distributed versions of Ligra and IrGL, where the distributed versions where created using Gluon. 
IrGL is a graph analysis framework utilizing a GPU. 
The results of the comparison were that Galois loads graphs faster, is faster than Gemini and Ligra at BFS and SSSP and depending on the graph either Ligra or Galois is the fastest at PR. 
In most cases distributed IrGL was the fastest of the tested frameworks. 
Galois and Ligra were shown to scale better on the number of nodes than Gemini.

Gemini puts itself against Ligra, Galois, PowerGraph, PowerLyra and GraphX \cite{Gemini}.
In a single-threaded scenario, Ligra was shown to be faster than both Galois and Gemini in SSSP and BFS applications. 
On the other hand, Gemini beat the other two in PR applications.
Furthermore, Gemini is presented to be one order of magnitude faster than PowerGraph, PowerLyra and GraphX on a multi-node computation unit.

The publication on Ligra is mainly about the multicore behaviour of Ligra rather than a comparison to other frameworks \cite{Ligra}.

Polymer provides a large set of comparisons to Galois, Ligra and X-Stream, all on a single computation node. In nearly all of their test cases, Polymer outperformed the other three frameworks \cite{Polymer}. 


